Model matters with restricted Boltzmann machines

### 2017-01-05 presentations/asu/slides.Rmd
add asu slides

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | December 20, 2016
  |
  | Slides available at <http://bit.ly/kaplan-umass>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "December 20, 2016"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

@@

* Slides -- <http://bit.ly/kaplan-umass>

>>>>

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | January 11, 2017
  |
  | Slides available at <http://bit.ly/kaplan-asu>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "January 11, 2017"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

@@

* Slides -- <http://bit.ly/kaplan-asu>
